### 2017-03-08 paper/intro.tex
pass

%%RQ3
Given the high execution cost associated with a significant number of
\github{} projects, we decided to investigate practical usage of test
suite parallelization.  It is important to note that modern build
systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
accelerate test execution (see Section~\ref{sec:modes}).  To find how
popular are these features in practice, we first analyzed build files
\emph{statically}.  Considering the +1m group of projects
(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
them use some parallelization option.  Considering those projects that
take more than 5m to run (\numLong{} in total), usage of parallelism
increases to 59\% (19/\numLong{}).  Furthermore, we found that
``forking'' virtual machines was the most prevalent parallel mode used
in practice.  This mode is used twice as much as any other mode used.
Important to note that ``forking VMs'' is perhaps the simplest of the
parallelization modes~--~it is provided by the build system as opposed
to the testing framework.  This result suggests that datarace
flakiness~\cite{luo-etal-fse2014} may be a concern to users as
``forking'' does not exploit thread-level concurrency within each VM,
which can create contention on data reachable from the static
area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
creates independent processes (\ie{}, Java VM instances) and executes
tests sequentially within each process. \Mar{why 32-19 did not use
  parallelization?} \Mar{what about free services (jenkins)?  how much
  can you scale execution and how expensive would that be?}

\Fix{...Discuss impact...}

>>>>

%%RQ3
Given the high execution cost associated with a significant number of
\github{} projects, we decided to investigate usage of test
suite parallelization in practice.  It is important to note that modern build
systems (\eg{}, Maven~\cite{maven}) offer parallelization options to
accelerate test execution (see Section~\ref{sec:modes}).  To find how
popular these features are in practice, we first analyzed build files
\emph{statically}.  Considering the $>$1m group of projects
(\numMedLong{} in total), we found that 49\% (41/\numMedLong{}) of
them use some parallelization option.  Considering those projects that
take more than 5m to run (\numLong{} in total), usage of parallelism
increases to 59\% (19/\numLong{}).  Furthermore, we found that
``forking'' virtual machines was the most prevalent parallel mode used
in practice.  This mode is used twice as much as any other mode used.
Important to note that ``forking VMs'' is perhaps the simplest of the
parallelization modes~--~it is provided by the build system as opposed
to the testing framework.  This result suggests that datarace
flakiness~\cite{luo-etal-fse2014} may be a concern to users as
``forking'' does not exploit thread-level concurrency within each VM,
which can create contention on data reachable from the static
area~\cite{bell-kaiser-icse2014,bell-etal-esecfse2015}.  Instead, it
creates independent processes (\ie{}, Java VM instances) and executes
tests sequentially within each process. \Mar{why 32-19 did not use
  parallelization?}

\Fix{...Discuss impact...}\Mar{what about free services (jenkins)?
  how much can you scale execution and how expensive would that be?}
